Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-06 nlpcc/paper.tex

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps:
\begin{enumerate}[1)]
    \item Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label. That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label;
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.
\end{enumerate}

In order to make all these encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title. (2) To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID, else number it with an new ID.

After the above steps, we acquire a list of instances and their unique IDs. Some of them contain cross-lingual information while some contain just monolingual information.

The process of unify class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.

>>>>

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps:
\begin{enumerate}[1)]
    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label. That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; 
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
\end{enumerate}

In order to make all encyclopedias link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese encyclopedias by instance title. (2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID, else number it with a new ID.

The process of unifying class and property is the same as instance. Meanwhile, all the relations in all sources are kept to prevent loss of information.
